---
title: "The **augmentedRCBD** package: A brief introduction"
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[LE,RO]{\slshape \rightmark}
- \fancyfoot[C]{\thepage}
- \usepackage{hyperref}
- \hypersetup{colorlinks=true}
- \hypersetup{linktoc=all}
- \hypersetup{linkcolor=blue}
- \usepackage{pdflscape}
- \usepackage{booktabs}
- \usepackage[table]{xcolor}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \fancyhead[LO,RE]{The augmentedRCBD package{:} A brief introduction}
output:
  pdf_document:
    dev: cairo_pdf
    fig_caption: no
  html_document:
    df_print: paged
csl: frontiers.csl
bibliography: REFERENCES.bib
link-citations: yes
toc: no
vignette: |
  %\VignetteIndexEntry{Introduction}
  %\usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown_notangle}
---
\begin{center}
 {\it J. Aravind\textsuperscript{1} , Mukesh Sankar S.\textsuperscript{2}}
\end{center}

\begin{center}
 Division of Germplasm Conservation, ICAR-National Bureau of Plant Genetic Resources, New Delhi
 Division of Genetics, ICAR-Indian Agricultural Research Institute, New Delhi
\end{center}

\begin{center}
`r Sys.Date()`
\end{center}

\begin{center}
\vspace{6pt}
\hrule
\end{center}

```{r, echo = FALSE}
knitr::opts_chunk$set(
  comment = "",
  fig.cap = ""
)
```


\tableofcontents

## Overview

## Installation
The package can be installed using the following functions:

```{r, eval=FALSE}
# Install from CRAN
install.packages('augmentedRCBD', dependencies=TRUE)

# Install development version from Github
devtools::install_github("aravind-j/augmentedRCBD")
```

Then the package can be loaded using the function
```{r}
library(augmentedRCBD)
```


## Testing

```{r}
# Example data
blk <- c(rep(1,7),rep(2,6),rep(3,7))
trt <- c(1, 2, 3, 4, 7, 11, 12, 1, 2, 3, 4, 5, 9, 1, 2, 3, 4, 8, 6, 10)
y1 <- c(92, 79, 87, 81, 96, 89, 82, 79, 81, 81, 91, 79, 78, 83, 77, 78, 78,
70, 75, 74)
y2 <- c(258, 224, 238, 278, 347, 300, 289, 260, 220, 237, 227, 281, 311, 250,
240, 268, 287, 226, 395, 450)
data <- data.frame(blk, trt, y1, y2)
# Convert block and treatment to factors
data$blk <- as.factor(data$blk)
data$trt <- as.factor(data$trt)
# Results for variable y1
out1 <- augmentedRCBD(data$blk, data$trt, data$y1, method = "lsd",
alpha = 0.05, group = TRUE, console = TRUE)
# Results for variable y2
out2 <- augmentedRCBD(data$blk, data$trt, data$y1, method = "lsd",
alpha = 0.05, group = TRUE, console = TRUE)
```

## Citing `augmentedRCBD`

```{r, echo = FALSE, collapse = TRUE}
suppressMessages(cit <- citation("augmentedRCBD"))
yr <- format(Sys.Date(), "%Y")
cit[1]$year <- yr
oc <- class(cit)

cit <- unclass(cit)
attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
                                     paste("\\(", yr, "\\)", sep = ""),
                                     attr(cit[[1]],"textVersion"))
class(cit) <- oc
cit
```


## Session Info

```{r}
sessionInfo()
```

## References
